---
title: "logloss - F1"
output: html_notebook
---


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r eval=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
source("config.R")
library(magrittr)
gc()
ret = read_csv(paste0('test-results/subtrain1', TODAY, ".csv"))
ret0 = ret %>% select(order_id,user_id, product_id, reordered, pred_reordered, order_number) 

```

order_number別のreorderの数値。予測が0.26くらいがfitするが、scoreは0.21のがかなり良。
```{r}
ret %>% rename(on = order_number) %>% group_by(on) %>% 
  summarise(
    n_items = n_distinct(product_id)/n_distinct(order_id)
    ,abv_thd = sum(reordered)/sum(pred_reordered>0.26)
    ,pred_rod_mean = mean(pred_reordered)
    ,actl_rod_mean = mean(reordered)
    ,pred_rod_n = pred_rod_mean * n_items
    ,actl_rod_n = actl_rod_mean * n_items
    ) %>%
  head(20)

```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
